Component-Based Framework of Lightweight Ruby for Efficient Embedded Software Development

### 2016-10-30 jssst/paper.tex
Modify the text by enago

The proposed framework is an extension of mruby on TECS framework \cite{par:mrubyonTECS}, and utilize two technologies i.e., mruby and TECS.
In this section, mruby (\ref{sec:mruby}), TECS (\ref{sec:TECS}), and mruby on TECS framework (\ref{sec:mruby on TECS}) are described.

@@

\subsection{mruby on TECS}
\label{sec:mruby on TECS}
mruby on TECS is a component-based framework for running an mruby script language on embedded systems.
This framework integrates two technologies, mruby and TECS, and enables to develop embedded software using script language without slowdown of the execution time.

@@

\begin{table}[t]
    \centering
\caption{Development procedure of existing and proposed framework}
    \scriptsize
    {\tabcolsep=0.1cm
    \begin{tabular}{c||c}
                            & Development procedure \\ \hline
        Exisiting framework &    (1) + (2) + (3)    \\ %\hline
        Proposed framework  &          (4)          \\ \hline
        \multicolumn{2}{l}{ (1): Rewrite the storage device} \\
        \multicolumn{2}{l}{ (2): Insert the storage device into the target} \\
        \multicolumn{2}{l}{ (3): Restart the RTOS on target (about 4 sec)} \\
        \multicolumn{2}{l}{ (4): Transfer an mruby bytecode from host to target} \\
    \end{tabular}
    }
    \label{tab:procedure}
\end{table}

@@

The Bluetooth loader for mruby bytecode can reduce the development time.
With the proposed framework, developers do not need to rewrite a storage/ROM device because only the bytecode should be transferred.
In the proposed framework, the development procedure is shortened as shown Table \ref{tab:procedure}
For example, with the existing system, when mruby programs are modified, developers must remove an SD card from the target device, connect the host PC, compile/link the platform, and reinsert the SD card in the target device in an experimental environment such as LEGO MINDSTORMS EV3.
In addition, the proposed framework eliminates the need to restart the target RTOS.
Note that the time of restarting the RTOS including initializing device drivers is 4 sec in case of  EV3 platform \cite{par:EV3}

@@

To execute multiple mruby applications, a synchronization mechanism for RiteVM tasks is implemented in the proposed framework.
We measured the time from the execution of the first RiteVM task to the execution of the last RiteVM task.
It was confirmed that the time was within the theoretical value. Theoretical value is 
\begin{displaymath}
    {\scriptsize periodic\ time \times (number\ of\ RiteVM\ tasks - 1)}
\end{displaymath}
Fig.\ref{fig:eval_synchronization} shows the case of two to eight RiteVM tasks.
% Fig.\ref{fig:eval_synchronization} shows the case of four RiteVM tasks.
% The periodic time is one msec, and the number of RiteVM is four.
Note that the periodic time is 1 msec.
As shown in Fig.\ref{fig:eval_synchronization}, the time is within the theoretical value respectively, which indicates successful synchronization of multiple RiteVM tasks.

@@

{\bf ChaiScript:} ChaiScript is a scripting language to be embedded in C++ applications.
It is a dialect of ECMAScript (a.k.a. JavaScript).
ChaiScript is header only, that is, it only needs to include the header files in order to use it in an application.
ChaiScript will support co-routines, but not now.

@@

Table \ref{tab:comparison} compares the proposed framework to previous methods.
The proposed framework implements all of the features shown in the table.
In particular, the proposed framework supports the loader, the VM scheduler, and application synchronization.
Note that the idea that a bytecode is transferred to the target device via Bluetooth can be applied scripting languages other than mruby if VM mechanism is used.

\section{Actual Results}
\label{sec:Results}
The proposed framework on LEGO MINDSTORMS EV3 \cite{url:download} has been certified for the official platform of ET Robocon 2016\footnote{http://www.etrobo.jp/2016/ (in Japanese)}.
In ET Robocon 2016, the team with the proposed framework took second place at a regional competition.

@@

\section{Conclusion}
\label{sec:Conclusion}
This paper presented an extended framework of mruby on TECS.
In the proposed framework, we implements a Bluetooth loader for mruby bytecode, a RiteVM scheduler, and synchronization mechanism.
The Bluetooth loader improves software development efficiency because of omitting the process to rewrite a storage/ROM device and restart an RTOS on a target device.
The loader can use both Bluetooth and a wired serial connection, thus the proposed framework can be applied to various embedded systems.
The RiteVM scheduler makes multitasking more user-friendly compared to the current mruby on TECS.
Our experimental results show the advantages of the proposed framework.
The Bluetooth loader can improve software development efficiency on mruby on TECS, and the RiteVM scheduler is effective in terms of execution time and ease of use compared to singletasking and co-routines.
In addition, synchronization of multiple RiteVM tasks is implemented in the proposed framework.

The proposed framework is developed using CBD.
In addition, the RiteVMs, RiteVM scheduler, and Eventflags are implemented as components; therefore, developers can add, remove, or reuse their functionalities easily as required.
Moreover, developers can choose fair scheduling or fixed-priority scheduling because the RiteVM scheduler can be added and removed easily.
For software developed with fixed-priority based scheduling, developers only have to remove the RiteVM scheduler.
% Component-based development can increase productivity.
Note that our prototype system and the application programs used in the performance evaluation are all open-source and can be downloaded from our website \cite{url:download}.

>>>>

The proposed framework is an extension of mruby on TECS framework \cite{par:mrubyonTECS}, and utilizes two technologies: mruby and TECS.
In this section, mruby (\ref{sec:mruby}), TECS (\ref{sec:TECS}), and mruby on TECS framework (\ref{sec:mruby on TECS}) are described.

@@

\subsection{mruby on TECS}
\label{sec:mruby on TECS}
mruby on TECS is a component-based framework for running an mruby script language on embedded systems.
This framework integrates two technologies, mruby and TECS, and enables to develop embedded software using a script language without slowing down the execution time.

@@

\begin{table}[t]
    \centering
\caption{Development procedure of existing and proposed frameworks}
    \scriptsize
    {\tabcolsep=0.1cm
    \begin{tabular}{c||c}
                            & Development procedure \\ \hline
        Exisiting framework &    (1) + (2) + (3)    \\ %\hline
        Proposed framework  &          (4)          \\ \hline
        \multicolumn{2}{l}{ (1): Rewrite the storage device} \\
        \multicolumn{2}{l}{ (2): Insert the storage device into the target} \\
        \multicolumn{2}{l}{ (3): Restart the RTOS on the target (about 4 sec)} \\
        \multicolumn{2}{l}{ (4): Transfer an mruby bytecode from host to target} \\
    \end{tabular}
    }
    \label{tab:procedure}
\end{table}

@@

The Bluetooth loader for mruby bytecode can reduce the development time.
With the proposed framework, developers do not need to rewrite a storage/ROM device because only the bytecode should be transferred.
In the proposed framework, the development procedure is shortened as shown Table \ref{tab:procedure}
For example, with the existing system, when mruby programs are modified, developers must remove an SD card from the target device, connect the host PC, compile/link the platform, and reinsert the SD card in the target device in an experimental environment such as LEGO MINDSTORMS EV3.
In addition, the proposed framework eliminates the need to restart the target RTOS.
Note that the time of restarting the RTOS, including initializing device drivers, is 4 sec in case of the EV3 platform \cite{par:EV3}

@@

To execute multiple mruby applications, a synchronization mechanism for RiteVM tasks is implemented in the proposed framework.
We measured the time from the execution of the first RiteVM task to that of the last RiteVM task.
It was confirmed that the time was within the theoretical value. Theoretical value is 
\begin{displaymath}
    {\scriptsize periodic\ time \times (number\ of\ RiteVM\ tasks - 1).}
\end{displaymath}
Fig.\ref{fig:eval_synchronization} shows the case of two to eight RiteVM tasks.
% Fig.\ref{fig:eval_synchronization} shows the case of four RiteVM tasks.
% The periodic time is one msec, and the number of RiteVM is four.
Note that the periodic time is 1 msec.
As shown in Fig.\ref{fig:eval_synchronization}, the time is within the theoretical value, which indicates successful synchronization of multiple RiteVM tasks.

@@

{\bf ChaiScript:} ChaiScript is a scripting language to be embedded in C++ applications.
It is a dialect of ECMAScript (a.k.a. JavaScript).
ChaiScript is header only, that is, it only needs to include the header files in order to be used it in an application.
ChaiScript will support co-routines, but not now.

@@

Table \ref{tab:comparison} compares the proposed framework to previous methods.
The proposed framework implements all of the features shown in the table.
In particular, the proposed framework supports the loader, the VM scheduler, and application synchronization.
Note that the idea that a bytecode is transferred to the target device via Bluetooth can be applied to scripting languages other than mruby if the VM mechanism is used.

\section{Actual Results}
\label{sec:Results}
The proposed framework on LEGO MINDSTORMS EV3 \cite{url:download} has been certified for the official platform of ET Robocon 2016\footnote{http://www.etrobo.jp/2016/ (in Japanese)}.
In ET Robocon 2016, the team with the proposed framework stood second in a regional competition.

@@

\section{Conclusion}
\label{sec:Conclusion}
This paper presented an extended framework of mruby on TECS.
In the proposed framework, we implement a Bluetooth loader for mruby bytecode, a RiteVM scheduler, and synchronization mechanism.
The Bluetooth loader improves the software development efficiency because of omitting the process to rewrite a storage/ROM device and restart an RTOS on the target device.
The loader can use both Bluetooth and a wired serial connection, thus the proposed framework can be applied to various embedded systems.
The RiteVM scheduler makes multitasking more user-friendly compared to the current mruby on TECS.
Our experimental results show the advantages of the proposed framework.
The Bluetooth loader can improve the software development efficiency of mruby on TECS, and the RiteVM scheduler is effective in terms of execution time and ease of use compared to singletasking and co-routines.
In addition, synchronization of multiple RiteVM tasks is implemented in the proposed framework.

The proposed framework is developed using CBD.
In addition, the RiteVMs, RiteVM scheduler, and Eventflags are implemented as components; therefore, developers can add, remove, or reuse their functionalities easily as required.
Moreover, developers can choose fair scheduling or fixed-priority scheduling because the RiteVM scheduler can be added and removed easily.
For software developed with fixed-priority-based scheduling, developers only have to remove the RiteVM scheduler.
% Component-based development can increase productivity.
Note that our prototype system and the application programs used in the performance evaluation are all open-source and can be downloaded from our website \cite{url:download}.
